---
title: "P8105 Homework 5: Iteration"
author: "Catherine Lucey (cml2270)"
date: "11/11/2021"
output: html_document
---

## Setup
Only done once, the setup code loads the necessary libraries and double checks that the working directory is correct. It also sets defaults for figure size with knitr, as well as a default theme and color scale for all ggplots.

```{r setup}
library(tidyverse)
library(readr)
getwd()

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

### Installing and Describing the WaPo Homicides Data

```{r}

urlfile = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

hom_df = read_csv(url(urlfile)) %>% 
   mutate(city_state = str_c(city, ", ", state))
  
```

The homicides dataset contains 53179 observations of 12 variables, these variables include LITERALLY HOW DO YOU DO THIS/???

```{r}

hom_df %>% 
 group_by(city_state, disposition) %>%
  summarise(n_unsolved = n()) %>% 
  #group_by(city_state, disposition) %>% 
  filter(disposition == "Closed without arrest" | 
           disposition == "Open/No arrest")

```

